Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-14 docs/ms.tex
Update ms.tex

One thing to note is that the conditional probability of $g$ in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
with $\vec{\alpha}$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
\begin{equation}
p(\vec{g}_{1}....\vec{g}_{n}|\vec{\alpha},Data)=p(\vec{g}_{1}|\vec{\alpha},Data_{1})....p(\vec{g}_{n}|\vec{\alpha},Data_{n})
\end{equation}
Therefore sampling reduced shear g from the conditional probability distribution can be reduced to a 2D sampling problem, which can be done very quickly.
In the Gibbs sampler, first we make a sample of $p(\vec{\alpha}|\vec{g},Data)$ with Metropolis-Hasting sampler. The we make samples of $g$ in different patches
independently according to formula (14).
The total time needed to sample $g$ and $\alpha$ of 64 sky patches with 8 galaxies in each patch is 
approximitly 25s on a 2 GHz CPU.

>>>>

One thing to note is that the conditional probability of $g$ in one patch only explicitly depends on $\alpha$, but not g in other patches. Therefore
with $\vec{\alpha}$ fixed, the posterior distributions of reduced shear in different patches are independent from each other. 
\begin{equation}
p(g_{1}....g_{n}|\vec{\alpha},Data)=p(g_{1}|\vec{\alpha},Data_{1})....p(g_{n}|\vec{\alpha},Data_{n})
\end{equation}
Therefore sampling reduced shear $g$ from the conditional probability distribution can be reduced to a 2D sampling problem, which can be done very quickly.
In the Gibbs sampler, first we make a sample of $p(\vec{\alpha}|\vec{g},Data)$ with Metropolis-Hasting sampler. The we make samples of $g$ in different patches
independently according to formula (14).
The total time needed to sample $g$ and $\vec{\alpha}$ of 64 sky patches with 8 galaxies in each patch is 
approximitly 25s on a 2 GHz CPU.
